Ricci and transit times

### 2014-12-19 prep_figures/commute/curvature-MCT.Rmd
access-distn WIP.

d5 <- get_results("../../results-rspr/commute-onesplit/123_45-1v5c.tsv")
d6 <- get_results("../../results-rspr/commute-onesplit/123_456-1v5c.tsv")
d <- d5[d5$MAT < 1000,]

>>>>

d5 <- get_results("../../results-rspr/commute-onesplit/123_45-1v5c.tsv")
d6 <- get_results("../../results-rspr/commute-onesplit/123_456-1v5c.tsv")
d <- d5[d5$MAT < 1000,]
d <- d6[d6$MAT < 1000,]
